\section{Design Rationale}

\subsection{Initial Research}

\subsubsection{Rating Usability of User Interfaces}
Based on the Shneiderman's Principles of Interaction Design, Don Norman's Design Principles and Tog's First Principles of Interaction Design, the following criteria have be identified as a solid starting point for any user interface:

\begin{itemize}
\item Consistency;
\item Informative feedback to the user;
\item Straightforward reversal of actions;
\item Promoting internal locus of control;
\item Low short-term memory load;
\item High feature visibility;
\item Information readability;
\end{itemize}

It was decided that rating some existing software that aims to achieve much of what is required by the specification for this assessment would provide a starting point for designing an application. A brief introduction to each of the analysed services and the analysis itself follows. 

\paragraph{AllRecipes} 
A website with a great diversity of content and a site that employs various forms 
of media to deliver information to its users. The site offers limited anonymous
use, restricted to browsing content only. With membership comes full access to 
site features, including the provisions for submitting recipes, uploading
photographs of completed dishes, saving recipes and creating shopping lists.

\paragraph{BigOven}: 
A website and application that runs on both Windows and mobile platforms, BigOven
boasts one of the largest recipe collections available online (250 000+). As well
as recipe organization and display, BigOven provides nutritional calculations,
an integrated meal planner, recipe importation, shopping list generators and even 
a cookbook creator.
\\*

\falseHeading{Analysis}

\paragraph{AllRecipes}
\begin{itemize}
\item \emph{Consistency:} The layout of the site is consistent across pages, with an identical header / navigation bar horizontal at the top and a panel placed at the right. A strong colour scheme is present throughout pages, and this is never broken. Features of the same / similar types take the same shape / size and emphasizing details, with even the advertisements placed in the same places on every page. The font features are established on the homepage and remain constant.
\item \emph{Feedback:} When manipulating recipes, a clear sense of what has been modified post-action is established through highly visible and concise feedback messages. The feedback messages do not intrude into the regular user experience.
\item \emph{Reversal of Actions:} Any modification of recipe settings is straightforward to undo via exactly the same process as was used to make the original change.
\item \emph{Internal Locus of Control: }The site generally performs well in this regard. Navigation is seamless and the user is afforded a strong idea of what will happen when an action is performed. Backend computation time is low, and in no circumstances does the site present the user with results that weren't suggested would be produced before carrying out an action.
\item \emph{Short-Term Memory Load:} Very low in that the site provides a wide range of options for preserving use state. Navigation is not heavily nested and so returning to a location typically requires very few actions.
\item \emph{Feature Visibility:} Features are very distinct from each other whilst being logically grouped, with focus being directed in a logical fashion through size, grouping and stylesheet effects.
\item \emph{Information Readability:} Font face is standard, although colour and sizing are problematic at times. Light font colours on a light background coupled with small font sizes (in places, particularly the side panel) can make some information difficult to read. Primary information highly visible, though.
\end{itemize}

\paragraph{BigOven}
\begin{itemize}
\item \emph{Consistency:} Core site layout is maintained across the board, but the 'body layout' changes between pages and this causes confusion. Lack of an ability to predict where content will be placed based on previous pages. A colour scheme is consistent throughout the site, as are font details.
\item \emph{Feedback:} Poor feedback on user interaction on the whole. Sometimes feedback is misleading, most of the time it is not at all visible and there isn't much of an attempt to highlight changes made by users to recipe views. 
\item \emph{Reversal of Actions:} Reversal of changes made to recipe views is straightforward, executed via the same actions that were used to instigate the initial changes. Difficult to discern successful revert due to bad feedback.
\item \emph{Internal Locus of Control:} Although the user is making changes to content and initiating computation, slow action processing times and poor feedback combine to cause a feeling that the user is waiting on the site to produce difficult to interpret results.
\item \emph{Short-Term Memory Load:} Not an issue, with light navigation and plenty of use state storage options.
\item \emph{Feature Visibility:} The site makes most features very visible, and there is often nothing to distract from features which should take user focus. Grouping, shape and size are employed well.
\item \emph{Information Readability:} Information is generally very readable. There are no issues with fonts or text sizing, and the colour scheme is well-chosen. The feedback after user actions can get in the way of important information in the recipes, as it isn't differentiated from the body text of the recipe.
\end{itemize}

\falseHeading{Layout Research}

\paragraph{Chosen Websites}
\begin{itemize}
\item finecooking.com
\item bbc.co.uk/food/recipes
\item jamieoliver.com/recipes
\item bbcgoodfood.com/recipes
\item uktv.co.uk/food/homepage/sid/423
\end{itemize}

\paragraph{Common Features}
\begin{itemize}
\item The front pages of all chosen sites had some sort of 'featured recipes' / 'recent recipes' element which more-or-less consumed the whole of the body space of that page. 
\item The chosen sites all had a 'related recipes' feature on pages where recipes were being browsed.
\end{itemize}

\paragraph{Individual Features}

\subparagraph{finecooking.com}
\begin{itemize}
\item Recipes are browsable using 'overlapping' categories, e.g. 'Ingredient', 'Course' etc.
\item Recipe navigation elements give concise information about the dish, e.g. suitability for vegetarians, preparation time.
\item Recipes are essentially a 'text dump' with a list of ingredients place at the top of the body.
\end{itemize}

\emph{bbc.co.uk/food/recipes}
\begin{itemize}
\item Preparation instructions are separated into distinct steps, with ingredients displayed first.
\item Recipes can be browsed by ingredients that they contain.
\item A 'Favourite Recipes' feature is provided.
\item A filterable search is provided.
\end{itemize}

\emph{jamieoliver.com/recipes}
\begin{itemize}
\item Confusing front-page layout, with multiple navigation bars and oversized images.
\item Recipes are again just a 'text dump'.
\item Ingredients spacing makes reading require a lot of scrolling.
\end{itemize}

\emph{bbcgoodfood.com/recipes}
\begin{itemize}
\item A summary of important information about the recipe is displayed at the top of recipe viewing pages.
\item Three column layout for recipe pages is confusing, no clear focus.
\end{itemize}

\emph{uktv.co.uk/food/homepage/sid/423}
\begin{itemize}
\item Featured recipes links on the home page don't navigate directly to the recipe.
\item Recipe page layout is pleasant: picture and important information at the top, ingredients and instructions side-by-side beneath the image and information with clear distinction between ingredients and instructions.
\end{itemize}

\subsection{Personas \& Scenarios}
From both the initial reasearch into other services and group discussion about the specification, many personas and scenarios were devised. The purpose of these was to both identify the potential users of the system to be designed and to aid in the formation of formal functional requirements. The personas and scenarios follow.

\paragraph{Jennifer}
\subparagraph{Persona}
Jennifer is a first-year student in History at the University of York. She is 
living on her own for the first time, and after spending the first term eating
primarily frozen dinners and instant noodles, she has decided it is time to 
learn how to cook for herself. Jennifer is computer-literate, and in fact quite
savvy on the web, but has little experience with kitchen appliances or utensils.
\subparagraph{Scenario}
Jennifer decides to cook a nice but fairly easy meal for herself and her 
housemates. Earlier in the day, she browses through the recipe website, looking
for fairly simple-looking recipes with cheap and easily-available ingredients.
Then, she goes to her local supermarket, navigates to the recipe on her phone,
and walks round picking up ingredients, checking off items in the recipe as she
buys them. She then checks how long it will take to cook the recipe, so she can
start at the right time, and heads off to a lecture.

That evening, she sets up her laptop in the kitchen to look at the recipe,
the easiest-to-follow view of the recipe, and starts cooking. She starts by 
measuring out all the ingredients she will need, and then starts working through
the individual steps. At one point, her housemates come into the kitchen and 
start up a conversation. She joins in, and when she returns to cooking realises
that she has forgotten where she was in the recipe. Fortunately, she was
checking off recipe steps as she did them, and the recipe site helps her find
where she left off to continue cooking.

\paragraph{Dale}
\subparagraph{Persona}
Dale is a 45 year-old headmaster at a primary school. He has been cooking at home
since he was about nine years old, being able to make complex meals for dinner
parties since he was sixteen. He revels in trying out new recipes and the more
complex the better. He regularly uses an iPad at home, including in the kitchen
where he has access to all of the latest cookery apps and blogs.
\subparagraph{Scenario}
Dale is planning a dinner party and would like ideas on what to cook. One of his
guests is vegetarian and so Dale would like to make sure that at least on of the
dishes that he prepares is suitable for vegetarians.He also needs to know (roughly) 
how long the meal will take to complete as he needs to be ready in time for his 
guests' arrival.

\paragraph{Bob}
\subparagraph{Persona}
Bob is a 16 year-old student. He aspires to become a professional cook after he 
finishes school and experiments with cooking as much as he can. He often prepares
dinners for his family and sometimes even his friends. Bob likes finding new
recipes on the internet and always looks for meals that would test his abilities.
\subparagraph{Scenario}
Bob has decided to make a meat pie for his grandmother. On his way back from 
school he picks up the groceries that he thinks he'll need for the pie. Bob finds
a suitable recipe using the app. The app allows him to choose his expertise level
and informs him that it affects how the recipe is displayed. He chooses 'expert'
at first, but midway through Bob realizes that it's a bit too hard to follow and
decides he would like to change to the 'intermediate' view. After the change, he
has no trouble finishing the meat pie.

\paragraph{Mike}
\subparagraph{Persona}
Mike is a 52 year-old store clerk. He is recently divorced and didn't really have
to worry about cooking until this point in his life. Mike can't afford to eat
take-away food anymore so he is trying to learn how to cook for himself. He knows
his way around a computer, but is not completely confident with technology.
\subparagraph{Scenario}
Mike decides to make an omelette one evening for himself. He finds a fairly 
simplistic, easy to follow recipe using the app and ther goes to a store to get
the required ingredients. When he comes back home, he realizes that he absent
mindedly shut off his device running the app, however when he loads up the 
app after booting up the device he notices that the app has recorded his 
recent activity and he has no trouble finding the omelette recipe again. He
follows the instructions and successfully finishes preparing the dish.

\paragraph{Mavis}
\subparagraph{Persona}
Mavis is a 65 year-old retiree, living alone. She has been cooking the same set 
of meals with a high-level of skill for the majority of her life, and has
decided that now she has a lot of time on her hands she would like to develop
her repertoire. She would also like to use this time to get up to speed with 
mobile technology, having never owned so much as a cell phone in the past.
\subparagraph{Scenario}
Mavis has decided to purchase a tablet to improve her relationship with modern
technology. One of the first apps that she asks her daughter to install for her
is the recipe app, so that she can get started with trying out some new recipes
without the need to pore over lots of cookery books. Mavis is completely 
unfamiliar with interacting with tablet devices, and would like an interactive 
tutorial process to 'show her the ropes' that doesn't appear to patronize her.

\paragraph{Andy}
\subparagraph{Persona}
Andy is a young man in his early twenties, who is comfortable in the kitchen but
mostly cooks simple and straightforward food. He dislikes cooking from recipe
books, but resorts to them for more complex meals and those with which he is
unfamiliar. He tends to speed-read recipes, often skipping steps or executing
instructions in the 'wrong' order, but is normally able to 'wing it' and produce
something reasonable.
\subparagraph{Scenario}
Andy wants to cook a potato salad, but has no lemon or garlic to make the
gremolata. He navigates to the recipe app, and starts cooking in the narrative
view.

Partway through, he discovers that he's having trouble keeping track of what he
should be doing, so he switches the recipe to the step-by-step view, and
discovers that he has done two of the steps in a different order than the 
step-by-step view prescribes (the narrative view didn't specify an order). He
checks off the out-of-order step, and then continues with the recipe in the
order given, skipping the steps relating to the gremolata.

\subsection{Functional Requirements}
The functional requirements arrived upon through the above work are as follows:

\subsubsection{Recipe Browsing}
Users must be able to:
\begin{itemize}
\item search for recipes using a full or partial recipe name;
\item view a list of all recipes that are present in the application's database of recipes;
\item filter any list of recipes using specific filtration criteria.
\end{itemize}

\subsubsection{Recipe Viewing}
Users must be able to:
\begin{itemize}
\item see general information about a recipe both when browsing multiple recipes and when viewing a single recipe;
\item see the ingredients required to complete a recipe;
\item see the instructions that need to be followed in order to complete a recipe;
\item change the level of detail in which recipe instructions are presented to them;
\item set the default level of detail in which all recipe instructions are presented to them;
\item mark instructions as completed through some interation.
\end{itemize}

\subsection{Viewing a Recipe}
The following is the design rationale behind the first piece of complex functionality found in the produced application: the process of viewing a recipe.

When designing the recipe view we tried to maintain a strong sense of consistency to the page, all fonts are uniform within their respective page groups (see figure~\ref{dr1}). We decided against bolding the names of ingredients in the recipe instructions even though we do bold the ingredient amounts. We felt this would just introduce unnecessary clutter breaking the sense of consistency and perhaps provide a false feedforward suggesting to the the user that the name is pressable when it is not.

Similarly we maintained information readability by using consistent and readable font sizes and spacing. The only exception is the difference in spacing between ingredients and instructions, but we purposely break down the readability between the two to cement them as separate elements to the page.

With regards to the instructions we ensured adequate spacing between instructions especially within the step by step view (see figure~\ref{dr2}). We feel the spacing is not enough to make the user think it is not belonging to the same group and at the same time is sufficient enough to ensure low short-term memory load. The User may well be dipping in and out of reading the page and thus giving them information in small chunks will be beneficial.

We allowed for high feature visibility by ensuring the buttons to change the type of view are coloured differently to their surrounding elements (see figure~\ref{dr2}). Though their relative size is small we feel the colour difference is sufficient enough to draw attention to it without making it the main feature of the page.

The view buttons also allow the user to set a default view (see figure~\ref{dr2}), we did this to promote internal locus of control. We want our users to feel a sense of control when using the system.

The type buttons do not immediately provide straightforward reversal of action for the user, pressing a view button twice will not undo its action. We did this on purpose to stay inline with what our research of other websites has shown us, we think the user will not expect this behaviour and as the other buttons are in close proximity they will use those to undo the action.

We do provide an easy reverse for ticking instructions, as users would expect pressing the element again reverses the action. The ticking off feature has also been designed to have high feature visibility. Empty tick boxes are always present which already suggest to the user that they can be ticked off, but further to this when a step is moused over it is highlighted providing the extra feedforward to further clarify its functionality.

\subsection{Filtering Lists of Recipes}
The following is the design rationale behind the second piece of complex functionality found in the produced application: the process of filtering lists of recipes.

It was decided early on by our group that easy recipe browsing is a high priority for us. Most cooking websites have a high volume of recipes, therefore robust tools are needed. Our solution to this problem was the introduction of the filtering menu. The multiple available choices enable the site visitors to get especially specific with their recipe needs. It shows up whenever user is browsing the recipes or after performing a search.

While designing the filters we used Shneiderman’s Eight Golden Rules of Interface Design and Don Norman’s design principles.

Based on our research of other recipe websites and phone applications available on the web  we distilled the following available filter types and their selections were chosen as follows. First filter is Dish type, with available selection of Main, Salad, Side and Dessert. Next is Dietary restriction, which allows choosing between Vegetarian, Vegan, Kosher and Halal. We considered this especially important, since it caters to users with extremely varying tastes. Difficulty filter has the expected choices of Beginner, Intermediate and Advanced, making it easy for the site visitors to narrow down the selection to their desired skill level for the recipes. The serves allow the user to specify the number of portions that can be made with the recipe. The Time Up to field allows to choose the maximum time a recipe would take to prepare. The time and serves fields have placeholder text, further explaining what those fields accomplish in regards to the filtering system. This acts as an affordance and helps the user figure out what inputs are expected from him or her as can be seen in figure~\ref{dr3}

The filter menu and the recipes use the same gradient background so that the user would naturally associate the two. The filters work and look exactly the same on both browse page as well as on search results page (except the filtering is done on the search results, rather than the whole database). This provides expected consistency between the pages, which means that the user has to figure out how to use the filters only one.

The filter menu takes up prominent space in the page to immediately draw attention to it. This is done with the intention of making sure that the user does not miss this important part of the website. This acts in accordance with Don Norman’s principles.

The reset button takes back the filter to its default state as well resetting the the recipe results. Both the filter and the reset buttons are made to look obviously clickable, which acts as an affordance as described in Don Norman’s Design Principles. The filters immediately react to changes by the user, offering immediate feedback on the performed operation. This also supports the internal locus of control rule described by Shneiderman. After a filtering operation is performed, the filter menu choices previously made are still visible in the menu. This allows for easy adjustments and also reduces the short term memory load while browsing the recipes, because the user does not have to remember the choices made previously.

If after filtering there are no recipes found a helpful message shows up saying that the search came up with no results as illustrated in figure~\ref{dr4}. This means that the user understands what’s happening and shows that the website is still functioning correctly. This is in accordance with the 3rd rule ‘Offer Informative Feedback’ from  Shneiderman’s Eight Golden Rules of Interface Design. 

The results themselves are displayed in the middle of the screen and are designed to be the centerpiece of the website. There is clear separation between individual results while still maintaining visual consistency. The recipes are displayed as information cards, ideally providing enough information at a glance to make an informed choice. This was inspired from our research done on popular cooking web sites available online. Each recipe is clearly separated from each to avoid confusion, however there is still visual consistency amongst them. Clicking on a recipe card leads to the full view of a recipe. To make this obvious, the recipe cards were designed to look like clickable buttons.