\documentclass{article}
\usepackage[utf8]{inputenc}

\title{IAPT Group 12 - Meeting Logbook}
\date{SPR/SUM 2014}

\begin{document}

\maketitle
\clearpage

\section*{12-02-2014}
\vspace{.5cm}
\emph{Attendees: }David Morris, Killian Murphy, Tadas Paliulis, Zain Razi.
\\
\emph{Absent: }N/A.

\begin{itemize}
\item Communication: 
  \begin {itemize}
  \item Discussed possible version control systems, decided on git repository hosted with GitHub with synchronisation with the CS SVN. 
  \item Discussed potentially making use of other tools to support reliablity and maintainability.
  \item Mailing list established.
  \item Shared calendar set up.
  \end{itemize}
\item Design and Prototyping:
  \begin{itemize}
  \item Discussed need for personae and scenarios, all to produce one persona and three scenarios for next meeting.
  \item Discussed prototyping techniques, all to produce paper wireframes for next meeting.
  \end{itemize}
\item Knowledge:
  \begin{itemize}
  \item Discussed knowledge requirements for assessment, all to review design principles and accessibility guidelines before next meeting.
  \end{itemize}
\item Responsibilities:
  \begin{itemize}
  \item KM assigned responsibility of maintaining meeting logs.
  \item DM assigned responsibility of converting recipes to HTML.
  \end{itemize}
\end{itemize}

\clearpage

\section*{17-02-2014}
\vspace{0.5cm}
\emph{Attendees: }David Morris, Killian Murphy, Tadas Paliulis, Zain Razi.
\\
\emph{Absent: }N/A.

\begin{itemize}
\item Prototyping:
  n  \begin{itemize}
  \item Discussed paper wireframes, all to be scanned and pushed to repository by 19-02-2014.
  \end{itemize}
\item Personae \& Scenarios:
  \begin{itemize}
  \item Discussed personae and scenarios devised since last meeting. All to be collated and pushed to repository by 19-02-2014.
  \end{itemize}
\item Coding:
  \begin{itemize}
  \item DM to start skeletal 'backend'.
  \end{itemize}
\item Responsibilities:
  \begin{itemize}
  \item ZR assigned responsibility of formalizing requirements.
  \item TP assigned responsibility of usability analysis of recipe websites.
  \item DM assigned responsibility of completing recipe to HTML conversion.
  \item KM assigned responsibility of design research, looking at existing related apps.
  \end{itemize}
\item Skype meeting on 19-02-2014;
\end{itemize}

\clearpage

\section*{24-02-2014}
\vspace{0.5cm}
\emph{Attendees: }David Morris, Killian Murphy, Tadas Paliulis, Zain Razi.
\\
\emph{Absent: }N/A

\begin{itemize}
\item Recipes:
  \begin{itemize}
  \item DM has produced recipes in plain text, YAML and HTML, with scripts to parse YAML and produce HTML. Pushed to repository.
  \end{itemize}
\item Design research:
  \begin{itemize}
  \item KM has produced usability assessment of relevant sites / apps. Pushed to repository.
  \item TP has produced design / layout assessment of relevant sites.
  \end{itemize}
\item Functional requirements:
  \begin{itemize}
  \item ZR has produced a list of essential functional requirements for the app.
  \end{itemize}
\item Wireframes:
  \begin{itemize}
  \item Formal wireframes needed to move forward. LucidChart decided on as the tool to be used for producing these wireframes.
  \end{itemize}
\item Responsibilities:
  \begin{itemize}
  \item All to produce formal wireframes by 26-02-2014 for a group session where final wireframes for initial prototype will be produced.
  \end{itemize}
\item Groupwork session scheduled for 26-02-2014, 1400.
\end{itemize}

\clearpage

\section*{26-02-2014}
\vspace{0.5cm}
\emph{Attendees: }David Morris, Killian Murphy, Tadas Paliulis, Zain Razi.
\\
\emph{Absent: }N/A

\begin{itemize}
\item Wireframes:
  \begin{itemize}
  \item All have produced wireframes for discussion.
  \item Layouts for three core pages discussed and decided upon.
  \end{itemize}
\item Responsibilities:
  \begin{itemize}
  \item KM to produce wireframes in Lucid Chart.
  \item KM to start work on implementing wireframes in HTML/CSS/JS.
  \item DM, ZR, TP to start work on implementing data layer.
  \end{itemize}
\item Next meeting scheduled for 05-03-2014.
\end{itemize}


\clearpage

\section*{05-03-2014}
\vspace{0.5cm}
\emph{Attendees: }David Morris, Killian Murphy, Tadas Paliulis, Zain Razi.
\\
\emph{Absent: }N/A

\begin{itemize}
\item Prototype Backend:
  \begin{itemize}
  \item DM has produced a simple schema, scripts to initialise and fill the database, and some PHP code to manipulate the database.
  \item A concrete schema must be decided upon before moving further with the backend - this to be produced on 07-03-2014.
  \end{itemize}
\item Prototype Frontend:
  \begin{itemize}
  \item KM has produced first iteration of frontend prototype.
  \item Group in agreement that it is of acceptable quality, some minor revisions suggested.
  \end{itemize}
\item Responsibilities:
  \begin{itemize}
  \item ZR / TP to devise domain object representation of recipe.
  \item KM to implement suggested revisions to frontend.
  \end{itemize}
\item Next meeting scheduled for 07-03-2014.
\end{itemize}

\clearpage

\section*{07-03-2014}
\vspace{0.5cm}
\emph{Attendees: }David Morris, Killian Murphy, Tadas Paliulis, Zain Razi.
\\
\emph{Absent: }N/A

\begin{itemize}
\item Backend:
  \begin{itemize}
  \item Concrete schema discussed and decided upon. 
  \item DM implemented schema and scripts to refill database with data to suit the new schema.
  \item PHP code needed to integrate front and back ends.
  \end{itemize}
\item Frontend: 
  \begin{itemize}
  \item KM implemented revisions suggested in previous meeting.
  \item Group in agreement that revisions are satisfactory.
  \end{itemize}
\item Heuristic Evaluation:
  \begin{itemize}
  \item Agreed upon that the CHE should occur before the end of SPR term.
  \item Target set for 12-03-2014 for the CHE.
  \end{itemize}
\item Responsibilities:
  \begin{itemize}
  \item KM to produce PHP code to integrate front and back ends by 12-03-2014.
  \item ZR, TP to prepare to conduct CHE on 12-03-2014.
  \end{itemize}
\item Groupwork session scheduled for 12-03-2014, 1400.
\end{itemize}

\clearpage

\section*{12-03-2014}
\vspace{0.5cm}
\emph{Attendees: }David Morris, Killian Murphy, Tadas Paliulis, Zain Razi.
\\
\emph{Absent: }N/A

\begin{itemize}
\item Heuristic Evaluation:
  \begin{itemize}
  \item The CHE was carried out as planned.
  \item The write-up of the CHE was discussed.
  \item Project issue-tracker was populated with issues unearthed by the CHE.
  \end{itemize}
\item Vacation Work:
  \begin{itemize}
  \item Communication schedule for the Easter vacation was discussed and decided upon.
  \item Work to be carried out during the Easter vacation was discussed.
  \end{itemize}
\item Responsibilities:
  \begin{itemize}
  \item ZR to carry out write-up of CHE.
  \item KM to resolve majority of app issues.
  \item DM to sanitize database data.
  \item TP to produce new recipe data.
  \end{itemize}
\item Next meeting scheduled for 17-04-2014.
\end{itemize}

\clearpage

\section*{17-03-2014}
\vspace{0.5cm}
\emph{Attendees: }Killian Murphy, Tadas Paliulis, Zain Razi
\\
\emph{Absent: }David Morris (Vacation)

\begin{itemize}
\item CHE Write-Up:
  \begin{itemize}
  \item ZR completed half of the CHE write-up.
  \end{itemize}
\item Recipe Data:
  \begin{itemize}
  \item TP has completed half of the new recipes in appropriate formats.
  \end{itemize}
\item App Issues:
  \begin{itemize}
  \item KM has resolved the majority of app issues in the issue-tracker.
  \end{itemize}
\item Responsibilities:
  \begin{itemize}
  \item ZR to complete second half of CHE write-up.
  \item TP to create additional recipes in appropriate formats.
  \item KM to resolve remaining app issues in issue tracker.
  \end{itemize}
\end{itemize}
\item Next meeting scheduled for 21-03-2014.
\end{itemize}

\clearpage

\section*{21-03-2014}
\vspace{0.5cm}
\emph{Attendees: }Killian Murphy, Tadas Paliulis, Zain Razi.
\\
\emph{Absent: }David Morris (Vacation).

\begin{itemize}
\item CHE Write-up:
  \begin{itemize}
  \item ZR has completed CHE write-up, is awaiting final app screenshots from KM.
  \end{itemize}
\item Recipe Data:
  \begin{itemize}
  \item TP has completed 12 new recipe files in appropriate formats.
  \end{itemize}
\item App Issues:
  \begin{itemize}
  \item KM has resolved all remaining issues in the issue-tracker.
  \end{itemize}
\item Repsonsibilities:
  \begin{itemize}
  \item KM to provide ZR with final screenshots for CHE write-up.
  \item TP to merge new recipe data onto master branch.
  \item KM to improve application search functionality.
  \end{itemize}
\item Next meeting scheduled for 25-03-2014.
\end{itemize}

\clearpage

\section*{25-03-2014}
\vspace{0.5cm}
\emph{Attendees: }David Morris, Killian Murphy, Tadas Paliulis.
\\
\emph{Absent: }Zain Razi (Vacation).

\begin{itemize}
\item Recipe Data:
  \begin{itemize}
  \item New recipe data needs to be incorporated into current database initialisation scripts.
  \item Specifically, new YAML files need to be correctly processed to extract all schema-required data.
  \end{itemize}
\item App Hosting:
  \begin{itemize}
  \item Application needs to be hosted in its current state such that all group members can access it.
  \item Changes to app need to be merged onto master branch of repository.
  \end{itemize}
\item Task-Based User Evaluation:
  \begin{itemize}
  \item TBUE needs to be designed ready for carrying out.
  \end{itemize}
\item Responsibilities:
  \begin{itemize}
  \item DM to make required changes to database initialisation.
  \item KM to host app and merge changes onto repository master branch.
  \item TP to begin designing TBUE.
  \end{itemize}
\item Next meeting scheduled for 21-04-2014 due to parallel workload of group members.
\end{itemize}

\clearpage

\section*{21-04-2014}
\vspace{0.5cm}
\emph{Attendees: }David Morris, Killian Murphy, Tadas Paliulis, Zain Razi.
\\
\emph{Absent: }N/A

\begin{itemize}
\item Roadmap:
  \begin{itemize}
  \item Schedule for time between 21-04-2014 and deadline was discussed and drawn up.
  \end{itemize}
\item App Modifications:
  \begin{itemize}
  \item Possible modifications to the web app were suggested by DM, discussed, and added to the development schedule.
  \end{itemize}
\item Task-Based User Evaluation:
  \begin{itemize}
  \item TP has completed design of TBUE.
  \item TBUE scheduled for 23-04-2014, 1200.
  \end{itemize}
\item Design Documentation:
  \begin{itemize}
    \item Spefics of design rationale discussed.
    \item Formalization of design notes discussed and added to the development schedule.
  \end{itemize}
\item Responsibilities:
  \begin{itemize}
    \item DM to implement proposed changes to app.
    \item DM to formalize maintainability documentation.
    \item KM to restructure existing documentation.
    \item KM to convert CHE write-up into TeX.
    \item TP & ZR to begin formalizing design notes.
  \end{itemize}
\item Next meeting scheduled for 23-04-2014.
\end{itemize}

\end{document}
